Linear instability underlying synchronous waving of marine grass in flow

### 2014-09-21 Paper/grass.tex
more update with MAHA comments and figures

\begin{abstract}
We show that the threshold flow condition for the spontaneous waving of marine grass arises due to the drag exerted by the vegetation on the flow. 
We show this by developing a self-consistent model of the flow past rigid vegetation. 
Linear stability analysis of the steady flow resulting from this model naturally leads to the threshold condition, and explains its mechanistic origin. 
Asymptotic analysis of the model for dense grass reveals two unstable modes. 
One of these modes shares many common features with the Kelvin-Helmholtz instability, but is demonstrated to be different from it. 
The predictions of the model for threshold condition and the resulting dominant frequency of waving agree with laboratory observations. 
\end{abstract}
\maketitle
%\section{Introduction}
Sea grasses exhibit a rich set of dynamical behavier due to their
 collective interaction with both steady and oscillatory flows. 
%interaction with the flow of water and can considerably affect surrounding hydrodynamic conditions.
%Resulting 
The resulting changes in hydrodynamic conditions can influence number of environmental processes such as transport of sediments, contaminants, dissolved oxygen, plant growth, and biomass production \cite{Fonseca87,Grizzle96,Nepf99,Nepf2012}.
The simplet response of these flexible grass canopies 
%Flexible grass canopies respond 
to steady currents 
%in the form of 
is the formation of coherent large amplitude oscillations, known as \monami \cite{AckermanOkubo93}. 
%Such motion is considered to play a central role in the recruitment 
%of microscopic marine organisms, such as blue mussel larvae\cite{Grizzle96}.
%The hydrodynamic mechanism underlying \monami is the focus of this paper. 
In this letter we provide a hydrodynamic mechanism for the onset of these coherent oscillations.

>>>>

\begin{abstract}
We show that the threshold flow condition for the spontaneous waving of marine grass arises due to the drag exerted by the vegetation on the flow. 
We show this by developing a self-consistent model of the flow past rigid vegetation. 
Linear stability analysis of the steady flow resulting from this model naturally leads to the threshold condition, and explains its mechanistic origin. 
Asymptotic analysis of the model for dense grass reveals two unstable modes. 
One of these modes shares many common features with the Kelvin-Helmholtz instability, but is demonstrated to be different from it. 
The predictions of the model for threshold condition and the resulting dominant frequency of waving agree with laboratory observations. 
\end{abstract}
\maketitle
%\section{Introduction}
Sea grasses exhibit a rich set of dynamical behavior due to their
 collective interaction with both steady and oscillatory flows. 
%interaction with the flow of water and can considerably affect surrounding hydrodynamic conditions.
%Resulting 
The resulting changes in hydrodynamic conditions can influence number of environmental processes such as transport of sediments, contaminants, dissolved oxygen, plant growth, and biomass production \cite{Fonseca87,Grizzle96,Nepf99,Nepf2012}.
The simplest response of these flexible grass canopies 
%Flexible grass canopies respond 
to steady currents 
%in the form of 
is the formation of coherent large amplitude oscillations, known as \monami \cite{AckermanOkubo93}. 
%Such motion is considered to play a central role in the recruitment 
%of microscopic marine organisms, such as blue mussel larvae\cite{Grizzle96}.
%The hydrodynamic mechanism underlying \monami is the focus of this paper. 
In this letter we provide a hydrodynamic mechanism for the onset of these coherent oscillations.
